Forecasting the 2024 US Presidential Election: A Poll-Based Approach

### 2024-10-30 paper/paper.qmd
Updated llm usage for survey and methodology design

>>>>

# **Appendix: Methodology and Survey Design for 2024 U.S. Presidential Election Forecast**

---

## **Appendix A: Methodology**

This section details the **idealized methodology** used to conduct a national survey to forecast the 2024 U.S. presidential election. The methodology includes **sampling strategies, recruitment methods, data validation techniques, and poll aggregation** procedures.

---

### **1. Sampling Approach**

- **Total Sample Size**: 10,000 respondents
- **Distribution by State**:
  - **Minimum 100 respondents per state** (including Washington, D.C.) to ensure balanced regional representation.
  - **Oversampling in battleground states** (e.g., Georgia, Pennsylvania, Arizona) with **1,000 respondents per state** for more precise insights.

- **Stratified Random Sampling**:
  - Stratify by **age, gender, race/ethnicity, education, income, and region**.
  - Ensure proportional representation based on **U.S. Census data** to avoid bias.

- **Weighting Strategy**:
  - Apply **post-stratification weighting** to adjust for any sampling imbalance, aligning with national demographics.

---

### **2. Recruitment Plan**

- **Recruitment Channels**:
  - Use **YouGov, Qualtrics**, and **MTurk** to access pre-screened online panels.
  - Complement with **social media ads** on Facebook, Instagram, and LinkedIn to reach underrepresented groups.

- **Incentives**:
  - Offer **$10 gift cards** or entry into sweepstakes to increase participation and engagement.

---

### **3. Survey Implementation and Design**

- **Survey Platform**: Google Forms  
  - **Link**: *(Insert Google Forms survey link here)*  
  - Accessible to respondents via **email, social media, and direct recruitment channels**.

- **Survey Structure**:
  1. **Demographics Section**: Age, gender, race/ethnicity, income, education, and state of residence.
  2. **Voting Preferences Section**: Candidate choice, likelihood of voting, and party affiliation.
  3. **Key Issues Section**: Identify priority issues (e.g., economy, healthcare, immigration).
  4. **Thank You Message**:  
     - *“Thank you for completing the survey! Your input is greatly appreciated and will help provide insights into the upcoming 2024 election.”*

---

### **4. Data Validation**

- **Techniques for Data Quality**:
  1. **Screening Questions**: Confirm eligibility (e.g., 18+ years old, registered voter status).
  2. **Attention Checks**: Include a question like *“Please select ‘Agree’ for this item”* to verify respondents are attentive.
  3. **IP Geolocation**: Validate state residency based on reported location.
  4. **Duplicate Detection**: Identify and remove duplicate responses.

---

### **5. Poll Aggregation and Reporting**

- **Poll Aggregation**:  
  - Combine results with data from **YouGov, Marquette, and other reliable sources** for a robust forecast.
  - Use **weighted averages** to account for differences in sample size and demographics.

- **Margin of Error**:  
  - **National Margin of Error**: ±1% at the 95% confidence level.  
  - **State-Level Margins**: ±5-10% depending on the sample size for each state.

---

### **6. Budget Allocation**

| **Expense**                     | **Estimated Cost**  |
|----------------------------------|---------------------|
| Panel Provider Fees              | $60,000             |
| Participant Incentives           | $20,000             |
| Social Media Advertising         | $10,000             |
| Google Forms (Platform)          | Free                |
| Data Validation & Analysis       | $8,000              |
| Miscellaneous Expenses           | $2,000              |
| **Total**                        | **$100,000**        |

---

## **Appendix B: Survey Questions**

Below is the full content of the survey to be implemented using Google Forms:

### **Survey Questions**

#### **Section 1: Demographics**
1. **What is your age?**  
   - 18-24  
   - 25-34  
   - 35-44  
   - 45-54  
   - 55-64  
   - 65+

2. **What is your gender?**  
   - Male  
   - Female  
   - Non-binary/Other

3. **What is your race/ethnicity?** (Select all that apply)  
   - White  
   - Black or African American  
   - Hispanic or Latino  
   - Asian  
   - Indigenous (Native American, Alaska Native, or First Nations)  
   - Pacific Islander or Native Hawaiian  
   - Other (please specify)

4. **What is your household income?**  
   - Less than $25,000  
   - $25,000 - $49,999  
   - $50,000 - $99,999  
   - $100,000 or more

5. **Which state do you currently reside in?**  
   - (List all 50 states + Washington, D.C.)

---

#### **Section 2: Voting Preferences**
6. **Are you a registered voter?**  
   - Yes  
   - No  
   - Not sure

7. **How likely are you to vote in the 2024 presidential election?**  
   - Definitely will vote  
   - Probably will vote  
   - Probably will not vote  
   - Definitely will not vote

8. **If the 2024 election were held today, who would you vote for?**  
   - Kamala Harris (Democrat)  
   - Donald Trump (Republican)  
   - Other (Please specify)  
   - Undecided

9. **How favorable are your opinions of the following candidates?**  
   (Rate on a scale of 1 to 5)  
   - Kamala Harris  
   - Donald Trump  
   - Any third-party candidates

---

#### **Section 3: Key Issues**
10. **What is the most important issue for you in this election?**  
   - Economy  
   - Healthcare  
   - Immigration  
   - Climate change  
   - Social Security and Medicare  
   - Foreign policy

11. **Which candidate do you think would handle the economy better?**  
   - Kamala Harris  
   - Donald Trump  
   - Not sure

---

#### **Thank You Message**
*“Thank you for completing the survey! Your input is greatly appreciated and will help provide insights into the upcoming 2024 election.”*

---

## **Appendix C: Google Forms Link**

Once the survey is created, insert the **Google Forms link** here for participants to access.

https://forms.gle/2MGYeZavDsCNuWZ1A
